|

### 2021-01-16 supplementary_information.Rmd
Update supplementary_information.Rmd

1. We listed recorded fish species and re-organized species names to be consistent across the data sets.
1. We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve unidentified species that are rarely observed in the data set (< 100 sites occurrence).
1. For sites with multiple visits (i.e., temporal replicates), we used the latest-year observation at each sampling site to minimize variation in sampling efforts among sites. Surveys that occurred in the same year were aggregated into a single observation.
1. We confined sites to those with the latest observation year of $\ge$ 1990. Although the data set contained observations from 1953, we added this restriction to align the observation period with the data set in the Midwest, US.
1. Four genera (Lethenteron, Pungitius, Rhinogobius, and Tribolodon) were treated as species groups (i.e., spp.) as taxonomic resolutions varied greatly among data sources.

>>>>

1. We listed recorded fish species and re-organized species names to be consistent across the data sets. Species that are identified at the family-level were removed.
1. We selected sampling sites based on the following criteria: (1) surveys were conducted with netting and/or electrofishing, (2) surveys were designed to collect a whole fish community, (3) sites contained reliable coordinates (sites with coordinates identical at 3 decimal degrees were treated as the same site), and (4) sites did not involve unidentified species that are rarely observed in the data set (< 100 sites occurrence).
1. For sites with multiple visits (i.e., temporal replicates), we used the latest-year observation at each sampling site to minimize variation in sampling efforts among sites. Surveys that occurred in the same year were aggregated into a single observation.
1. We confined sites to those with the latest observation year of $\ge$ 1990. Although the data set contained observations from 1953, we added this restriction to align the observation period with the data set in the Midwest, US.
1. Four genera (Lethenteron, Pungitius, Rhinogobius, and Tribolodon) were treated as species groups (i.e., spp.) as they are difficult to identify and taxonomic resolutions varied greatly among data sources.
